### 2017-01-17 text/Chapter01.tex
Edits pages 95-124

\paragraph{The thesis.}
The key claim of this thesis is that the theory of \emph{coeffects} that we develop provides
a unified way of capturing how programs rely on the context, or execution environment, 
in which they execute. Perhaps most importantly, coeffects provide a single conceptual framework 
that can capture a wide range of previously disconnected notions of context-awareness.

@@

\item In Chapter~\ref{ch:semantics} we give categorical semantics of the flat coeffect calculus.
  This provides a unified way of defining the semantics of context-aware languages. We use the
  categorical semantics as a basis for \emph{categorically-inspired translation} that turns
  context-aware programs into programs in a simple functional language. We prove that well-typed
  context-aware programs are translated to programs that ``do not go wrong''. The development
  is repeated for structural coeffects in Chapter~\ref{ch:structural}.

>>>>

\paragraph{The thesis.}
Our key claim is that the theory of \emph{coeffects} that we develop in this thesis provides
a uniform and less error-prone way of writing programs that rely on the context, or
execution environment, in which they run. Perhaps most importantly, coeffects provide a single 
conceptual framework that can capture a wide range of previously disconnected notions of 
context-awareness and thus make understanding of context easier.

@@

\item In Chapter~\ref{ch:semantics} we give categorical semantics of the flat coeffect calculus.
  This provides a unified way of defining the semantics of context-aware languages. We use the
  categorical semantics as a basis for \emph{categorically-inspired translation} that turns
  context-aware programs into programs in a simple functional language. We prove that well-typed
  context-aware programs are translated to programs that ``do not get stuck''. The development
  is repeated for structural coeffects in Chapter~\ref{ch:structural}.
